Revisions Analyses & Figures

### 2023-09-19 Revisions_Analyses&Figures.Rmd
Added updated plots, demographics, variable importance code

library(tidymodels) # machine learning metaverse
library(xgboost) # main engine, needs version 1.0.0.2, see above
library(effectsize)
```

@@

#followup_brainage <-
#  fit_workflow_followup %>%
#  predict(new_data = analysis_sample_baseline) %>%
#  mutate(
    # provide the chronological age at time of scan
#    truth = analysis_sample_baseline$interview_age
 # ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
 # mutate(gap = .pred - truth)
```
# model features and importance
```{r}
# vip plot of feature importance
library(vip)

@@

vi(abcd_model_obj_combat)

@@

#Cortical - Area
dk_vi_area <- abcd_vi_renamed_dk %>%
  filter(grepl('Area', Variable)) %>% 
  filter(label != "") %>% 
  select(Importance,label)

@@

summary(lm.beta(followup_puberty_y_mod2))

@@

@@

ggplot(abcd_brainage_pds_followup_combat, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#BDB5D5", alpha=.25)+
  geom_abline(a=0, b=1, color='#233D4D') +
  xlim(1, 22) + # 5, 20
  ylim(1, 22) +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))

@@

ggplot(both_mods_baseline, aes(x=truth, y=corrected_pred, group=model, col=model, fill=model)) +
     # geom_point() +
  geom_jitter(alpha=.2) +
  #geom_abline(a=0, b=1, color='#233D4D') +
  #xlim(8, 15) + # 5, 20
 # ylim(8, 15) +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))

@@

ggplot(both_mods_followup, aes(x=truth, y=corrected_pred, group=model, col=model, fill=model)) +
     # geom_point() +
  geom_jitter(alpha=.2) +
  #geom_abline(a=0, b=1, color='#233D4D') +
  #xlim(8, 15) + # 5, 20
 # ylim(8, 15) +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))

@@

### Rerun old figures
```{r}
# Distrubutions of puberty/cognition by model

@@

@@

```{r}
# correlation between gaps from waves, or something more complicated?
# maybe multilevel model so that it's nested by participant? - 
# correlation for vlad's models

#correlation for abcd models

# figure - probably spaghetti plot, show direction of gap change

>>>>

library(tidymodels) # machine learning metaverse
library(xgboost) # main engine, needs version 1.0.0.2, see above
library(effectsize)
library(psych)
library(ggpubr)
library(vip)
```

@@

#followup_brainage <-
#  fit_workflow_followup %>%
#  predict(new_data = analysis_sample_baseline) %>%
#  mutate(
    # provide the chronological age at time of scan
#    truth = analysis_sample_baseline$interview_age
 # ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
 # mutate(gap = .pred - truth)
```

# model features and importance
```{r}
# vip plot of feature importance
library(vip)

## from model code

final_xgb_combat %>%
  fit(data = df_train) %>%
  extract_fit_parsnip() %>%
  vip(geom = "point")

fit_workflow_combat %>%
  fit(data = df_train) %>%
  extract_fit_parsnip() %>%
  vi()

###

vip(abcd_model_obj_combat, num_features = 175)

@@

vi_updated <- vi(abcd_model_obj_combat)

vi(fit_workflow_combat)

vi_updated2 <- vi(extract_fit_parsnip(fit_workflow_combat))

#vi_model(abcd_model_obj_combat)

@@

#Cortical - Area
dk_vi_area <- abcd_vi_dk %>%
  filter(grepl('Area', Variable)) %>% 
  filter(label != "") %>% 
  select(Importance,label)

@@

summary(lm.beta(followup_puberty_y_mod2))
```

# Descriptive Table
```{r}
describe(brainage_pds_baseline_combat)

describe(brainage_pds_followup_combat)

describe(abcd_brainage_pds_baseline_combat)

describe(abcd_brainage_pds_followup_combat)
```
# New Demographics Column for Follow- Up (Model 2)
```{r}
nrow(abcd_brainage_pds_followup_combat %>% filter(sex == "F")) / nrow(abcd_brainage_pds_followup_combat)
nrow(abcd_brainage_pds_followup_combat %>% filter(sex == "M")) / nrow(abcd_brainage_pds_followup_combat)

demographics <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/pdem02.txt") %>%
  filter(!collection_title=="collection_title") %>% 
  select(src_subject_id, contains("demo_race"), demo_ethn_v2, demo_ethn2_v2, demo_comb_income_v2)

demographics_baseline_abcdmodel <- left_join(abcd_baseline, demographics)

demographics_long <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_lpds01.txt") %>%
  filter(!collection_title=="collection_title") %>% 
  select(src_subject_id, eventname, demo_comb_income_v2_l)

demographics_baseline_abcdmodel <- left_join(demographics_baseline_abcdmodel, demographics_long %>% filter(eventname == "baseline_year_1_arm_1"))

#family income
table(demographics_baseline$demo_comb_income_v2)

#Overall values
#Non-hispanic white
demographics_baseline %>% 
  filter(demo_race_a_p___10 == 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Non-hispanic Black
demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 == 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Hispanic
demographics_baseline %>% 
  filter(demo_ethn_v2 == 1)

demographics_baseline %>% 
  filter(((demo_race_a_p___10 == 1 | demo_race_a_p___11 == 1) & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1) & demo_ethn_v2 == 1)

#Asian
demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & ( demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Native American Alaska Native
demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & (demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 )

#Multiracial

# mutate column: true if participant marked any asian category
# mutate column: true if participant marked native american/alaska native
# sum white, black, asian, native american/alaska native, and additional races

demographics_baseline %>% 
  mutate_at(c(18:33), as.numeric) %>% 
  mutate(
    demo_race_asian = case_when((demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) ~ 1,
                            (demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1) ~ 0),
         demo_race_native_american_alaskan = case_when((demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) ~ 1,
                                                       (demo_race_a_p___12 !=1 & demo_race_a_p___13 != 1) ~ 0),
         race_total = rowSums(across(c(demo_race_a_p___10, demo_race_a_p___11, demo_race_a_p___14, demo_race_a_p___15, demo_race_a_p___16, demo_race_a_p___17, demo_race_a_p___25, demo_race_asian, demo_race_native_american_alaskan)), na.rm=T)) %>% 
  filter(race_total > 1)

#additional races
#If the caregiver chose Native Hawaiian, Guamanian, or Samoan, Other Race, or refused to choose a racial category, the youth was placed in the “additional” race group as there were too few youth in each of these categories individually for separate analysis.

demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)

@@

## Rerun prediction plots
```{r}
## Baseline - Model 1
baseline_pred_mod1_plot <- ggplot(brainage_pds_baseline_combat, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#A1C181", alpha=.2) +
  geom_abline(a=0, b=1, color='#233D4D') +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_pred_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

baseline_gap_mod1_plot <- ggplot(brainage_pds_baseline_combat, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#A1C181", alpha=.2)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_gap_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(baseline_pred_mod1_plot, baseline_gap_mod1_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave(filename = "pred_bias_baseline_mod1_combat.png",
                          width=10, height=5, units='in', dpi=300)

## Follow-Up - Model 1
followup_pred_mod1_plot <- ggplot(brainage_pds_followup_combat, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#619B8A", alpha=.2)+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_pred_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
followup_gap_mod1_plot <- ggplot(brainage_pds_followup_combat, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#619B8A", alpha=.2)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_gap_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Panel Plots
ggarrange(baseline_pred_mod1_plot, baseline_gap_mod1_plot, followup_pred_mod1_plot, followup_gap_mod1_plot, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

ggsave(filename = "pred_bias_mod1_combat.png",
                          width=10, height=10, units='in', dpi=300)

## Baseline - Model 2
baseline_pred_mod2_plot <- ggplot(abcd_brainage_pds_baseline_combat, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#E76F51", alpha=.25)+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_pred_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
baseline_gap_mod2_plot <- ggplot(abcd_brainage_pds_baseline_combat, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#E76F51", alpha=.25)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_gap_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

# Follow-Up - Model 2
# '#C8A2C8', '#856088','#702963', '#800080'
followup_pred_mod2_plot <- ggplot(abcd_brainage_pds_followup_combat, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#856088", alpha=.25)+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="followup_truth_corrected_pred_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
followup_gap_mod2_plot <- ggplot(abcd_brainage_pds_followup_combat, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#856088", alpha=.25)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="followup_truth_corrected_gap_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Panel Plots
ggarrange(baseline_pred_mod2_plot, baseline_gap_mod2_plot, followup_pred_mod2_plot, followup_gap_mod2_plot,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

ggsave(filename = "pred_bias_mod2_combat.png",
                          width=10, height=10, units='in', dpi=300)

@@

ggplot(abcd_brainage_pds_followup_combat, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#BDB5D5", alpha=.25)+
  geom_abline(a=0, b=1, color='#233D4D') +
  xlim(1, 22) + # 5, 20
  ylim(1, 22) +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
```

@@

# Model 1 = light green "#A1C181"
# Model 2 = red "#E76F51"

ggplot(both_mods_baseline, aes(x=truth, y=corrected_pred, group=model, col=model, fill=model)) +
  geom_jitter(alpha=.2) +
  scale_color_manual(values = c("#A1C181", "#E76F51")) +
  #geom_abline(a=0, b=1, color='#233D4D') +
  #xlim(8, 15) + # 5, 20
 # ylim(8, 15) +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))

@@

# model 1: blue/teal "#619B8A"
# model 2 : purple "#856088"

ggplot(both_mods_followup, aes(x=truth, y=corrected_pred, group=model, col=model, fill=model)) +
  geom_jitter(alpha=.2) +
  scale_color_manual(values = c("#619B8A", "#856088")) +
  #geom_abline(a=0, b=1, color='#233D4D') +
  #xlim(8, 15) + # 5, 20
 # ylim(8, 15) +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))

@@

### Rerun old figures
```{r}
# Distributions of puberty/cognition by model
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
categorical_pds_baseline_combat <-  brainage_pds_baseline_combat %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         cognition_cat=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 85, 115, Inf), labels=c(">-1", "-1-1", ">1")),
         cognition_cat_small=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 92, 108, Inf), labels=c(">-.5", "-.5-.5", ">.5")),
         cog_quart = cut(nihtbx_totalcomp_uncorrected, quantile(nihtbx_totalcomp_uncorrected, na.rm=T), labels=c("0-25", "25-50", "50-75", "75-100")))
#don't z-score, include more than 1 standard deviation and less than 1 standard deviation (ignore within 1 SD)

#Youth-Report Puberty
youth_pds_baseline_mod1_plot <- ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))),  #,'#526D37'
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend = 8) +
  theme(text = element_text(size = 12)) 
ggsave(filename="baseline_youth_pds_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Parent-Report Puberty
parent_pds_baseline_mod1_plot <- ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend = 8) +
  theme(text = element_text(size = 12)) 
ggsave(filename="baseline_parent_pds_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Cognition
ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(cognition_cat) & cognition_cat!="-1-1" ) %>% 
  ggdensity(x = "corrected_gap", color= "cognition_cat", fill="cognition_cat", add="mean", palette = c('#7CA352',
 '#CCDDBB'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Standardized Cognition")  +
  theme(text = element_text(size = 24))

ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(cognition_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "cognition_cat", fill="cognition_cat", add="mean")), xlab="Brain Age Gap", ylab="Density", legend.title = "Age-Corrected Cognition")

ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(cognition_cat_small)) %>% 
  ggdensity(x = "corrected_gap", color= "cognition_cat_small", fill="cognition_cat_small", add="mean")), xlab="Brain Age Gap", ylab="Density", legend.title = "Age-Corrected Cognition (.5 sd")

#Cognition Quartiles
cog_baseline_mod1_plot <- ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(cog_quart) & cog_quart!="25-50" & cog_quart!="50-75" ) %>% 
  ggdensity(x = "corrected_gap", color= "cog_quart", fill="cog_quart", add="mean", palette = c('#7CA352',
 '#CCDDBB'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Quartiles)", font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_cognition_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_baseline_mod1_plot, parent_pds_baseline_mod1_plot, cog_baseline_mod1_plot, 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)

ggsave(filename = "distributions_baseline_mod1_combat.png",
                          width=7, height=5, units='in', dpi=300)

```
```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
categorical_pds_followup_combat <-  brainage_pds_followup_combat %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")))

#don't z-score, include more than 1 standard deviation and less than 1 standard deviation (ignore within 1 SD)

youth_pds_followup_mod1_plot <- ggpar((categorical_pds_followup_combat %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#B4D0C7','#82B0A2', '#619B8A', '#568A7B'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend=8)  +
  theme(text = element_text(size = 12))

ggsave(filename="followup_youth_pds_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Parent-Report Puberty
parent_pds_followup_mod1_plot <-ggpar((categorical_pds_followup_combat %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#B4D0C7','#82B0A2', '#619B8A', '#568A7B'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend=8)  +
  theme(text = element_text(size = 12))

ggsave(filename="followup_parent_pds_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_followup_mod1_plot, parent_pds_followup_mod1_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
ggsave(filename = "distributions_followup_mod1_combat.png",
                          width=10, height=4, units='in', dpi=300)

```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
abcd_baseline_categorical_pds_combat <- abcd_brainage_pds_baseline_combat %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         cognition_cat=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 85, 115, Inf), labels=c(">-1", "-1-1", ">1")),
         cognition_cat_small=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 92, 108, Inf), labels=c(">-.5", "-.5-.5", ">.5")),
         cog_quart = cut(nihtbx_totalcomp_uncorrected, quantile(nihtbx_totalcomp_uncorrected, na.rm=T), labels=c("0-25", "25-50", "50-75", "75-100")))

#don't z-score, include more than 1 standard deviation and less than 1 standard deviation (ignore within 1 SD)

#Youth-report puberty
youth_pds_baseline_mod2_plot <- ggpar((abcd_baseline_categorical_pds_combat %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#FCCA46','#F3B5A5', '#E76F51', '#B43718'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS",  font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_youth_pds_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Parent-Report Puberty
parent_pds_baseline_mod2_plot <- ggpar((abcd_baseline_categorical_pds_combat %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#FCCA46','#F3B5A5', '#E76F51', '#B43718'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_parent_pds_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggpar((abcd_baseline_categorical_pds_combat %>% 
  filter(!is.na(cognition_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "cognition_cat", fill="cognition_cat", add="mean", palette=c('#FCCA46',
 '#E76F51'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Standard Scores") +
  theme(text = element_text(size = 24))

ggpar((abcd_baseline_categorical_pds_combat %>% 
  filter(!is.na(cognition_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "cognition_cat_small", fill="cognition_cat_small", add="mean")), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Standard Scores) .5 SD") +
  theme(text = element_text(size = 24))

#Cognition Quartiles
cog_baseline_mod2_plot <- ggpar((abcd_baseline_categorical_pds_combat %>% 
  filter(!is.na(cog_quart) & cog_quart!="25-50" & cog_quart!="50-75" ) %>% 
  ggdensity(x = "corrected_gap", color= "cog_quart", fill="cog_quart", add="mean", palette = c('#FCCA46',
 '#E76F51'))), xlab="Brain Age Gap", ylab="Density", legend.title = "Cognition (Quartiles)", font.legend = 8)  +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_cognition_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_baseline_mod2_plot, parent_pds_baseline_mod2_plot, cog_baseline_mod2_plot, 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)
ggsave(filename = "distributions_baseline_mod2_combat.png",
                          width=7, height=5, units='in', dpi=300)

```
```{r}

####### UPDATE COLORS

#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
abcd_categorical_pds_followup_combat <-  abcd_brainage_pds_followup_combat %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")))

#don't z-score, include more than 1 standard deviation and less than 1 standard deviation (ignore within 1 SD)

youth_pds_followup_mod2_plot <- ggpar((abcd_categorical_pds_followup_combat %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette=c('#C8A2C8', '#856088','#702963', '#800080'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend=8)  +
  theme(text = element_text(size = 12))

ggsave(filename="followup_youth_pds_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

#Parent-Report Puberty
parent_pds_followup_mod2_plot <-ggpar((abcd_categorical_pds_followup_combat %>% 
  filter(!is.na(parent_pds_cat)) %>% 
ggdensity(x = "corrected_gap", color= "parent_pds_cat", fill= "parent_pds_cat", add="mean", palette=c('#C8A2C8', '#856088','#702963', '#800080'))), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Parent-Report PDS", font.legend=8)  +
  theme(text = element_text(size = 12))

ggsave(filename="followup_parent_pds_mod2_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggarrange(youth_pds_followup_mod2_plot, parent_pds_followup_mod2_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
ggsave(filename = "distributions_followup_mod2_combat.png",
                          width=10, height=4, units='in', dpi=300)

@@

```{r}
# Model feature - follow-up

# vip
abcd_model_obj_combat_followup <- fit_workflow_combat_followup$fit$fit$fit

vip(fit_workflow_combat_followup, num_features = 20)

vip(abcd_model_obj_combat_followup, num_features = 20)

vi(fit_workflow_combat_followup$fit$fit$fit)

abcd_vi_followup <- left_join(vi(abcd_model_obj_combat_followup), abcd_vi_renamed)

abcd_vi_dk_followup <- left_join(vi(abcd_model_obj_combat_followup), abcd_vi_renamed_dk)

#Cortical - Volume
dk_vi_vol_followup <- abcd_vi_dk_followup %>%
  filter(grepl('Vol', Variable)) %>% 
  filter(label != "") %>% 
  select(Importance,label)

dk_vi_vol_followup <- data.frame(dk_vi_vol_followup)

ggplot(dk_vi_vol_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance.png",
                         width=8, height=4, units='in', dpi=300)

#Cortical - Area
dk_vi_area_followup <- abcd_vi_dk_followup %>%
  filter(grepl('Area', Variable)) %>% 
  filter(label != "") %>% 
  select(Importance,label)

dk_vi_area_followup <- data.frame(dk_vi_area_followup)

ggplot(dk_vi_area_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance.png",
                         width=8, height=4, units='in', dpi=300)

#Subcortical
aseg_vi_followup <- abcd_vi_followup %>%
  filter(label != "") %>% 
  select(Importance,label)

aseg_vi_followup <- data.frame(aseg_vi_followup)

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal.png",
                          width=7, height=4, units='in', dpi=300)

@@

```{r}
# correlation between gaps from waves, or something more complicated?
# maybe multilevel model so that it's nested by participant? -

# correlation for vlad's models
# join baseline and follow-up corrected gaps by id
brainage_both_waves <- left_join(brainage_pds_baseline_combat %>% select(src_subject_id, corrected_pred, corrected_gap) %>% rename(baseline_pred = corrected_pred, baseline_gap = corrected_gap), brainage_pds_followup_combat %>% select(src_subject_id, corrected_pred, corrected_gap) %>% rename(followup_pred = corrected_pred, followup_gap = corrected_gap))

cor(brainage_both_waves$baseline_gap, brainage_both_waves$followup_gap, use="complete.obs")

cor.test(brainage_both_waves$baseline_gap, brainage_both_waves$followup_gap, use="complete.obs")

#correlation for abcd models
# join baseline and follow-up corrected gaps by id
brainage_abcd_both_waves <- left_join(abcd_brainage_pds_baseline_combat %>% select(src_subject_id, corrected_pred, corrected_gap) %>% rename(baseline_pred = corrected_pred, baseline_gap = corrected_gap), abcd_brainage_pds_followup_combat %>% select(src_subject_id, corrected_pred, corrected_gap) %>% rename(followup_pred = corrected_pred, followup_gap = corrected_gap))

cor(brainage_abcd_both_waves$baseline_gap, brainage_abcd_both_waves$followup_gap, use="complete.obs")

cor.test(brainage_abcd_both_waves$baseline_gap, brainage_abcd_both_waves$followup_gap, use="complete.obs")
```
